Testing the Waters: A Dive into Elevated Lead Levels in Toronto Homes

### 2024-01-25 outputs/paper/lead_concentration.qmd
Rename paper.qmd to lead_concentration.qmd

cleaned_data |>
  summarize(mean_lead_concentration_ppb = mean(lead_concentration_ppb),
    sd_lead_concentration_ppb = sd(lead_concentration_ppb)) |>
  kable(
    col.names = c("Mean Lead Concentration (ppb)", "SD of Lead Concentration (ppb)")
    )
```

>>>>

cleaned_data |>
  summarize(
    mean_lead_concentration_ppb = sprintf("%.2f", mean(lead_concentration_ppb)),
    sd_lead_concentration_ppb = sprintf("%.2f", sd(lead_concentration_ppb))
    ) |>
  kable(
    col.names = c("Mean Lead Concentration (ppb)", "SD of Lead Concentration (ppb)")
    )
```
